An open source scientific article

### 2021-10-21 src/ms.tex
syntax

\acknowledgments
The authors would like to thank the Astronomical Data Group at Flatiron for listening to every iteration of this project and for providing great feedback every step of the way.

>>>>

\begin{acknowledgments}
The authors would like to thank the Astronomical Data Group at Flatiron for listening to every iteration of this project and for providing great feedback every step of the way.
\end{acknowledgments}
